---
title: "Snippets"
author: "Dr K"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
##FinalData$treatment <- relevel(FinalData$treatment,ref="placebo")
FinalData$infected <- relevel(FinalData$infected,ref="OK")
guy = filter(FinalData, sex == "guy")
gal = filter(FinalData, sex == "gal")
gay = filter(FinalData, LGBTQ == "gay")
Druguser = filter(FinalData, DrugUser == "yes")
```

# Introduction  

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.

# Coding Details  

```{r}
Maledata <- filter(FinalData, sex == "guy")
Maledata$sex <- as.factor(Maledata$sex)
Maledata$treatment <- as.factor(Maledata$treatment)
```

```{r}
Femaledata <- filter(FinalData, sex == "gal")
Femaledata$sex <- as.factor(Femaledata$sex)
Femaledata$treatment <- as.factor(Femaledata$treatment)
```

```{r}
LGBTQdata <- filter(FinalData, LGBTQ == "gay")
LGBTQdata$sex <- as.factor(LGBTQdata$sex)
LGBTQdata$treatment <- as.factor(LGBTQdata$treatment)
```

```{r}
DrugUserdata <- filter(FinalData, DrugUser == "yes")
DrugUserdata$sex <- as.factor(DrugUserdata$sex)
DrugUserdata$treatment <- as.factor(DrugUserdata$treatment)
```

# Guys   

## Barplot   

```{r}
guy <- Maledata %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(guy,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(guy,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

the barchart is showing from the males who were infected with covid19 almost 58% were given the drug and about 42% received the placebo.


## Numerical Results    

```{r}
table1 <- xtabs(~treatment + infected, data=Maledata)
rowPerc(table1)
colPerc(table1)
print(table1)
```

this table shows that about 340 males were infected with covid-19 out of 10,450 males. this table also shows that 3.7% of the males who have received the drug contracted covid-19 while 2.5% of the males who received the placebo contracted covid-19 as well as the table shows that males who got the covid vaccine were almost 50% more likely to contract covid and because it's less that 60% that shows that the vaccine is not effective for males.


## Inferarential    

```{r}
chisq.test(table1)
chisqtestGC(table1)
guysfish <- fisher.test(table1)
guysfish
```

the p-value is a very tiny number. 
$H_0$ the null hypothesis is that the vaccine makes no difference in males when it comes to contracting the covid-19.

$H_0$ the alternative hypothesis is that the vaccine in fact makes a difference in whether or not a male contracts covid-19.

we will reject the null hypothesis. 


```{r}
effect <- guysfish$p.value/(guysfish$p.value  +1)
effectivenessguy =  guysfish$estimate/(guysfish$estimate+1)
print(effectivenessguy*100)
```

```{r}
low=(guysfish$conf.int[1]/(guysfish$conf.int[1] +1))
hi=(guysfish$conf.int[2]/(guysfish$conf.int[2] +1))
options(digits=2)
```

## ## Effectiveness Confidence Interval `r low`  to `r hi`



# Gals 

## Barplot


```{r}
gal <- Femaledata %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(gal,aes(x=infected,y= count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(gal,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

the barchart is showing from the females who were infected with covid19 almost 34% were given the drug and about 66% received the placebo.

## Numerical Results 

```{r}
table2 <- xtabs(~infected + treatment, data=Femaledata)
rowPerc(table2)
colPerc(table2)
print(table2)
```

this table shows that about 607 males were infected with covid-19 out of 8,606 females. this table also shows that 4.7% of the females who have received the drug contracted covid-19 while 8.7% of the females who received the placebo contracted covid-19 as well as the table shows that females who got the covid vaccine were almost 67% less likely to contract covid. that shows that the vaccine is effective for Females.

## Infrarertial 

```{r}
chisq.test(table2)
chisqtestGC(table2)
galsfish <- fisher.test(table2)
galsfish
```

the p-value is a very tiny number 
$H_0$ the null hypothesis is that the vaccine makes no difference in females when it comes to contracting the covid-19.

$H_0$ the alternative hypothesis is that the vaccine in fact makes a difference in whether or not a female contracts covid-19.

we will reject the null hypothesis. 

the vaccine is effective for females to be taken, because it is 67% effective and it's more than 60% which is effective. 

```{r}
effect <- galsfish$p.value/(galsfish$p.value  +1)
effectivenessgal = galsfish$estimate/(galsfish$estimate+1)
print(effectivenessgal*100)
```

```{r}
low=(galsfish$conf.int[1]/(galsfish$conf.int[1] +1))
hi=(galsfish$conf.int[2]/(galsfish$conf.int[2] +1))
options(digits=2)
```

## ## Effectiveness Confidence Interval `r low`  to `r hi`


# Gay sexual orintation 

## Barplot




```{r}
gay <- LGBTQdata %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(gay,aes(x=treatment,y=count,fill=infected))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(gay,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```


## Numerical Results
```{r}
table3 <- xtabs(~treatment + infected, data=LGBTQdata)
rowPerc(table3)
colPerc(table3)
print(table3)
```

## Infraretial 
```{r}
chisq.test(table3)
chisqtestGC(table3)
LGBTQfish <- fisher.test(table3)
LGBTQfish
```

this data shows that the covid vaccine is not effective in the LGBTQ population. 

```{r}
effect <- LGBTQfish$p.value/(LGBTQfish$p.value  +1)
effectivenessLGBTQ = LGBTQfish$estimate/(LGBTQfish$estimate+1)
print(effectivenessLGBTQ*100)
```

```{r}
low=(LGBTQfish$conf.int[1]/(LGBTQfish$conf.int[1] +1))
hi=(LGBTQfish$conf.int[2]/(LGBTQfish$conf.int[2] +1))
options(digits=2)
```

## ## Effectiveness Confidence Interval `r low`  to `r hi`

# People that are drugUsers

## Barplot

```{r}
yes <- DrugUserdata %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(yes,aes(x=infected,y= count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(yes,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

the barchart is showing out of 117 DrugUsers who were infected with covid19 almost 34% were given the drug and about 66% received the placebo.

## Numerical Results

```{r}
table3 <- xtabs(~infected + treatment, data=DrugUserdata)
rowPerc(table3)
colPerc(table3)
print(table3)
```

this table shows that about 117 drug users were infected with covid-19 out of 2,166 drug users. this table also shows that 33% of the drug users who have received the drug contracted covid-19 while 67% of the drug users who received the placebo contracted covid-19 as well as the table shows that drug users who got the covid vaccine were almost 65% less likely to contract covid. that shows that the vaccine is effective for drug users.

## Infrarertial 

```{r}
chisq.test(table3)
chisqtestGC(table3)
yesfish <- fisher.test(table3)
yesfish
```

the p-value is a very tiny number 
$H_0$ the null hypothesis is that the vaccine makes no difference in drug users when it comes to contracting the covid-19.

$H_0$ the alternative hypothesis is that the vaccine in fact makes a difference in whether or not a drug user contracts covid-19.

we will reject the null hypothesis. 

the vaccine is effective for drug users to be taken, because it is 65% effective and it's more than 60% which is effective as well as the odds ratio is 1.8. 


```{r}
effect <- yesfish$p.value/(yesfish$p.value  +1)
effectivenessyes = yesfish$estimate/(yesfish$estimate+1)
print(effectivenessyes*100)
```

```{r}
low=(yesfish$conf.int[1]/(yesfish$conf.int[1] +1))
hi=(yesfish$conf.int[2]/(yesfish$conf.int[2] +1))
options(digits=2)
```

## ## Effectiveness Confidence Interval `r low`  to `r hi`

# Discussions and Conclusions 

after viewing the four populations we found that 
